For submission to the Journal of Integrated Pest Management

### 2021-05-17 ofv_fife_2021.Rmd
Making more corrections to MS based on reviewers

*Orchid fleck dichorhavirus* (OFV) infects over 50 plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (Citrus). The only known vectors of dichorhaviruses are flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae). OFV was found infecting liriopogons (*Liriope* spp. and *Ophiopogon* spp.),  as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in the landscape in Leon County, Florida, during the summer of 2020. The presence of OFV was confirmed using OFV-specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing. RT-PCR amplicons had a 98% identity with known OFV sequences available in NCBI GenBank. Other leaf samples of the plant family Asparagaceae with ringspots and chlorosis were collected from Leon and Alachua counties and tested with PCR and Sanger sequencing to detect OFV. Identification of partial genome sequence from PCR products confirmed the presence of both OFV orchid strains (OFV-Orc1 and OFV-Orc2) in Florida. These strains of OFV are known to infect citrus and cause citrus leprosis disease. Three potential mite vectors were identified from OFV-infected plants using cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (sensu lato), *B. obovatus*, and *B. confusus*. Florida has various native and introduced plants in the landscape that Brevipalpus spp. feed on, which are potentially susceptible to OFV. In this study, we report three new hosts from the family Asparagaceae from multiple locations. Our data suggested that OFV is widely distributed in Florida and might be a threat for various plant species growing in the southeastern US.

@@

\pagebreak
*Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family Rhabdoviridae; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018]. Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the sole vectors of dichorhaviruses [@Maeda1998]. *Brevipalpus californicus* (Banks) sensu lato mites are the only group known to transmit OFV in a persistent propagative manner [@Kondo2003].

>>>>

*Orchid fleck dichorhavirus* (OFV) infects over 50 plant species belonging to the family Orchidaceae, Asparagaceae (Nolinoidaea), and Rutaceae (Citrus). The only known vectors of dichorhaviruses are flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae). OFV was found infecting liriopogons (*Liriope* spp. and *Ophiopogon* spp.),  as well as *Aspidistra elatior* Blume (Asparagaceae: Nolinoidaea) in the landscape in Leon County, Florida, during the summer of 2020. The presence of OFV was confirmed using OFV-specific conventional reverse transcription polymerase chain assay (RT-PCR) assay and Sanger sequencing. RT-PCR amplicons had a 98% identity with known OFV sequences available in NCBI GenBank. Other leaf samples of the plant family Asparagaceae with ringspots and chlorosis were collected from Leon and Alachua counties and tested with PCR and Sanger sequencing to detect OFV. Identification of partial genome sequence from PCR products confirmed the presence of both OFV orchid strains (OFV-Orc1 and OFV-Orc2) in Florida. These strains of OFV are known to infect citrus and cause citrus leprosis disease. Three potential mite vectors were identified from OFV-infected plants using cryo-scanning electron microscopy (Cryo-SEM): *Brevipalpus californicus* (sensu lato), *B. obovatus*, and *B. confusus*. Florida has various native and introduced plants in the landscape that *Brevipalpus* spp. feed on, which are potentially susceptible to OFV. In this study, we report three new hosts from the family Asparagaceae from multiple locations. Our data suggested that *Orchid fleck dichorhavirus* is widely distributed in Florida and might be a threat for various plant species growing in the southeastern US.

@@

\pagebreak
*Orchid fleck dichorhavirus* (OFV) is the type member for the genus *Dichorhavirus*, family *Rhabdoviridae*; a bacilliform, nuclear rhabdovirus composed of two segments of single-stranded, negative-sense RNA which infects plants [@Amarasinghe2019; @Dietzgen2014; @Walker2018]. Flat mites from the genus *Brevipalpus* Donnadieu (Trombidiformes: Tenuipalpidae) are the only known vectors of dichorhaviruses [@Maeda1998]. *Brevipalpus californicus* (Banks) sensu lato mites are the only group known to transmit OFV in a persistent propagative manner [@Kondo2003].
